An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-20 poly-embed-journal/poly-embed-journal.tex
final set of todos for poly-embed-journal??

\begin{abstract}
  \raf{prev title: An Embedding Framework for Consistent Polyhedral Surrogates}\jessie{I like the new title}

  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings\jessiet{this means nothing to a reader; do we want to say ``via embedding discrete predictions into the real coordinate space (of $d$ dimensions?)''... maybe merging with next sentence?  or ignore.}, for problems such as classification, ranking, or structured prediction. 
  In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
  We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses.
  Given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds. \jessiet{Switch order of this sentence and next?}
  Conversely, we show how to construct a consistent polyhedral surrogate for any given discrete loss.
  Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
  \raft{Insert sentence about regret bounds}
  We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
  Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
  % The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
\end{abstract}

@@

%% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
While a growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions, to date much of this work has been ad-hoc.
We lack general tools to systematically construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{need a good ref for multiclass; I'm thinking WW and others}\jessiet{Probably Crammer-Singer and One-vs-All as well?}.
This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one often requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
Clever constructions like the binary-encoded predictions (BEP) surrogate for multiclass classification with an abstain option~\cite{ramaswamy2018consistent}, which achieves logarithmic prediction dimension, are the exception rather than the rule.
In all of these settings, we lack a unifying framework that moves from a given target problem to a convex consistent surrogate and link function.

@@

For discrete prediction problems like classification, the given (discrete) loss is often computationally intractable to optimize directly.
Therefore, many machine learning algorithms instead minimize a surrogate loss function with better optimization qualities, such as convexity.
To ensure that this surrogate loss successfully addresses the original problem, one needs to establish statistical consistency, a minimal requirement that is a prerequisite for generalization bounds.
Consistency roughly says that, in the limit as one obtains more and more data, the learned hypothesis approaches the best possible.
Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to original\jessie{target?} reports.

\raft{Rewrote this section intro, and added a bunch here so the reader knows roughly how all these concepts connect.  Could use some eyes. \jessie{I like this second paragraph that wraps everything together}}
In this section, we introduce notation and concepts related to consistency that we use throughout.
Consistency is often a difficult condition to work with directly, but in finite prediction settings, it is equivalent the simpler notion of \emph{calibration} (Definition~\ref{def:calibrated}) which depends solely on the conditional distribution over the labels~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex}.
Even simpler than calibration indirect elicitation, a weaker condition only requiring that optimal surrogate reports link to optimal target reports.
Finally, we introduce a new precise notion of embedding, a special case of indirect elicitation, which forms the backbone of our approach.

@@

\begin{definition}[Directly Elicits]
  \label{def:elicits}
  A loss $L:\R\to\reals^\Y_+$, \emph{(directly) elicits} a property $\Gamma:\simplex \toto \R$ if
  \begin{equation}
    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
  If $L$ elicits a property, that property is unique and we denote it $\prop{L}$.
\end{definition}
Since we have defined a property $\Gamma$ to be nonempty, if the minimum \jessie{infimum?} of expected loss $\inprod{p}{L(\cdot)}$ is not attained for some $p \in \simplex$, then $L$ does not elicit a property.
We say that a loss $L$ is \emph{minimizable} if the infimum of $\inprod{p}{L(\cdot)}$ is attained for all $p \in \simplex$.
For example, hinge loss is minimizable, whereas logistic loss is not (take $p=(0,1)$ or $(1,0)$).

@@

\btw{Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

@@

We now define an embedding, which is a special case of indirect property elicitation.
(This fact is non-trivial; see Lemma~\ref{lem:embedding-implies-indirect-elic}.)
In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
\begin{definition}[Embedding]\label{def:loss-embed}
  A minimizable loss $L:\reals^d\to\reals^\Y_+$ \emph{embeds} a loss $\ell:\R\to\reals^\Y_+$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}.
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, excluding polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \cite{abernethy2013efficient} and in connections between proper losses and mechanism design \cite{frongillo2014general}.

@@

The key idea behind our construction is the notion of \emph{separation}, a condition which is equivalent to calibration for discrete prediction problems.
Roughly, given a surrogate $L$ and discrete target $\ell$, a link is $\epsilon$-separated if the distance between any $L$-optimal point in $\reals^d$, and any point that links to an $\ell$-suboptimal report, is at least $\epsilon$.
\raft{Changed; previous statement was not correct I think: ``Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.''}
We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.

@@

\begin{definition}[Separated Link]\label{def:sep-link}
  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
  We say a link $\psi:\reals^d\to\R$
  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
\end{definition}

@@

Applying Construction \ref{const:eps-thick-link} also enables one to verify the consistency of a given proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
\botodo{In general, how do we deal with the $\epsilon$? How do we know what $\epsilon$ to test? I guess we can gradually shrink it and see...}
\raft{A guess for $\epsilon$ was pretty clear from the top-$k$ paper, so yeah I think ``shrink and see'' makes sense.  Also probably okay to not even mention $\epsilon$ here given the last line of the paragraph.}
See \S~\ref{sec:top-k} for an illustration of this test.
On the other hand, if $\psi^*$ cannot be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.

Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
We illustrate this formulaic approach in \S~\ref{sec:abstain}.
\jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}

@@

%% giving intuition for abstain figure: how to use fig to find consistency restrictions
As an illustration, one can use the fact that $\BEP$ embeds $\ellabstain$ to verify that $\BEP$ is inconsistent for multiclass classification, i.e., with respect to 0-1 loss.
In particular, since the abstain report $\bot$ is $\ellabstain$-optimal whenever $\max_{y\in\Y} p_y \leq 1/2$, by the definition of embedding, the origin $0\in\reals^d$ is $\BEP$-optimal for the same distributions.
Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
\raft{I simplified this paragraph to reduce redundancy, and rewrote much of the figure caption so it's clearer how it applies more generally.  See what you think!}
\jessiet{I really like the caption now, but in the caption we're comparing $\prop{L}$ to $\prop{\ell}$ and in the paragraph we mention $\prop{\hat \ell}$, where $\hat \ell$ is the embedded loss.  I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...}
\raft{Good call -- that was the whole point after all!  I updated to include the embedded property.}
% , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$. 
% As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
% The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.

@@

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{tikz/lovasz-link-envelope.pdf}
		\end{minipage}\hfill
		\caption{Links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$. Points in each region link to the embedding point contained in the region. Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\raf{Almost there!  First $u_2$ is still small, and same for the coordinate labels in the third figure.  The lines in the first two are also much thicker compared to the third and to Figure~\ref{fig:abstain-links}.}
			}
			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?  Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better... let's discuss next call}}
		\label{fig:lovasz-links}
	\end{center}
\end{figure}

@@

\subsection{Trimming a loss}

@@

\subsection{Minimum representative sets and non-redundancy}

@@

\subsection{A property elicitation perspective on trimmed losses}

@@

Perhaps the most pressing open direction is simply to apply our framework to prediction problems of interest.
We hope that the discussion in \S~\ref{sec:apply-embedd-fram}, and the detailed examples in subsequent works, serve as useful guidelines for doing so.
A particularly promising domain to apply our framework is structured prediction, where relatively few consistent surrogates are known.
Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses\raft{Cite the two Nowak Rudi Bach papers; 2nd one came out now: \url{https://proceedings.mlr.press/v151/nowak22a.html}}.

@@

>>>>

\begin{abstract}
  \raft{FYI: prev title: An Embedding Framework for Consistent Polyhedral Surrogates\jessie{I like the new title}}
  \raft{FYI: Finally updated the abstract}
  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
  In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
  We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses:
  every discrete loss is embedded by some polyhedral loss, and every polyhedral loss embeds some discrete loss.
  Moreover, an embedding gives rise to a consistent link function as well as linear surrogate regret bounds.
  Our results are constructive, as we illustrate with several examples.
  In particular, our framework gives succinct proofs of consistency or inconsistency for various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
  We go on to show additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
  Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
  % The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
\end{abstract}

@@

%% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
While a growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions, to date much of this work has been ad-hoc.
We lack general tools to systematically construct consistent convex surrogates, much less an understanding of the full class of consistent surrogates.
For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{TODO: ref for multiclass; I'm thinking WW and others}\jessiet{Probably Crammer-Singer and One-vs-All as well?}\raft{Yep, let's add those}.
This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one often requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
Clever constructions like the binary-encoded predictions (BEP) surrogate for multiclass classification with an abstain option~\cite{ramaswamy2018consistent}, which achieves logarithmic prediction dimension, are the exception rather than the rule.
In all of these settings, we lack a unifying framework that moves from a given target problem to a convex consistent surrogate and link function.

@@

For discrete prediction problems like classification, the given (discrete) loss is often computationally intractable to optimize directly.
Therefore, many machine learning algorithms instead minimize a surrogate loss function with better optimization qualities, such as convexity.
To ensure that this surrogate loss successfully addresses the original target problem, one needs to establish statistical consistency, a minimal requirement that is a prerequisite for generalization bounds.
Consistency roughly says that, in the limit as one obtains more and more data, the learned hypothesis approaches the best possible.
Consistency depends crucially on the choice of link function that maps surrogate reports (predictions) to target reports.

In this section, we introduce notation and concepts related to consistency that we use throughout.
Consistency is often a difficult condition to work with directly, but in finite prediction settings, it is equivalent the simpler notion of \emph{calibration} (Definition~\ref{def:calibrated}) which depends solely on the conditional distribution over the labels~\citep{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex}.
Even simpler than calibration indirect elicitation, a weaker condition only requiring that optimal surrogate reports link to optimal target reports.
Finally, we introduce a new precise notion of embedding, a special case of indirect elicitation, which forms the backbone of our approach.

@@

\begin{definition}[Directly Elicits]
  \label{def:elicits}
  A loss $L:\R\to\reals^\Y_+$, \emph{(directly) elicits} a property $\Gamma:\simplex \toto \R$ if
  \begin{equation}
    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
  If $L$ elicits a property, that property is unique and we denote it $\prop{L}$.
\end{definition}
Since we have defined a property $\Gamma$ to be nonempty, if the infimum of expected loss $\inprod{p}{L(\cdot)}$ is not attained for some $p \in \simplex$, then $L$ does not elicit a property.
We say that a loss $L$ is \emph{minimizable} if the infimum of $\inprod{p}{L(\cdot)}$ is attained for all $p \in \simplex$.
For example, hinge loss is minimizable, whereas logistic loss is not (take $p=(0,1)$ or $(1,0)$).

@@

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

@@

We now define an embedding, which is a special case of indirect property elicitation.
(This fact is non-trivial; see Lemma~\ref{lem:embedding-implies-indirect-elic}.)
In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
As we discuss following Proposition~\ref{prop:representative-embeds-restriction}, this latter condition can be more simply stated: the representative set for the target must embed into a representative set for the surrogate.
\raft{FYI: Added this last sentence}
\begin{definition}[Embedding]\label{def:loss-embed}
  A minimizable loss $L:\reals^d\to\reals^\Y_+$ \emph{embeds} a loss $\ell:\R\to\reals^\Y_+$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

\raft{FYI: I added this paragraph since I used it in the Lov\'asz hinge talk (so I didn't have to define properties), and realized that maybe it should have been our definition this whole time!  I was terse with the details, but we could spell it out more if it's not clear.}
Proposition~\ref{prop:representative-embeds-restriction} reveals an equivalent definition of an embedding which can be more convenient.
Given a representative set $\Sc$ for $\ell$, an injection $\varphi:\Sc\to\reals^d$ is an embedding if: (i) the loss values match as in Definition~\ref{def:loss-embed}(i), and (ii) $\varphi(\Sc)$ is representative for $L$.
This new definition is clearly implied by Definition~\ref{def:loss-embed}; for the converse, Proposition~\ref{prop:representative-embeds-restriction} states that $L$ embeds $L|_{\varphi(\Sc)}$, which by (i) is the same loss as $\ell$ up to relabeling via $\varphi$.

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}.
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, excluding polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \cite{abernethy2013efficient} and in connections between proper losses and mechanism design \cite{frongillo2014general}.

@@

The key idea behind our construction is the notion of \emph{separation}, a condition which is equivalent to calibration for discrete prediction problems.
Roughly, given a surrogate $L$ and discrete target $\ell$, a link is $\epsilon$-separated if the distance between any $L$-optimal point in $\reals^d$, and any point that links to an $\ell$-suboptimal report, is at least $\epsilon$.
\raft{FYI: previous statement was not correct I think: ``Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.''}
We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.

@@

\begin{definition}[Separated Link]\label{def:sep-link}
  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
  We say a link $\psi:\reals^d\to\R$
  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
  \raft{FYI, this def, along with Theorem~\ref{thm:discrete-loss-poly-embeddable} and Theorem~\ref{thm:calibrated-separated}, are referenced specifically from the top-k paper, so hopefully the numbers don't change by the time we post on arXiv}
\end{definition}

@@

Applying Construction \ref{const:eps-thick-link} also enables one to verify the consistency of a given proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.
On the other hand, if $\psi^*$ cannot be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.

Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
We illustrate this formulaic approach in \S~\ref{sec:abstain}.
\jessiet{I'm a little confused by (the intention of) this paragraph, but could just be me.}
\raft{Yeah, we could cut it, but given that we wrote it in response to a reviewer back in the day, I think it's fine to keep too. \#burn}

@@

%% giving intuition for abstain figure: how to use fig to find consistency restrictions
As an illustration, one can use the fact that $\BEP$ embeds $\ellabstain$ to verify that $\BEP$ is inconsistent for multiclass classification, i.e., with respect to 0-1 loss.
In particular, since the abstain report $\bot$ is $\ellabstain$-optimal whenever $\max_{y\in\Y} p_y \leq 1/2$, by the definition of embedding, the origin $0\in\reals^d$ is $\BEP$-optimal for the same distributions.
Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
\jessiet{I really like the caption now, but in the caption we're comparing $\prop{L}$ to $\prop{\ell}$ and in the paragraph we mention $\prop{\hat \ell}$, where $\hat \ell$ is the embedded loss.  I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$... \raf{Good call -- that was the whole point after all!  I updated to include the embedded property. \#burn if it looks good.}}
% , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$. 
% As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
% The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.

@@

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{tikz/lovasz-link-envelope.pdf}
		\end{minipage}\hfill
		\caption{Links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$. Points in each region link to the embedding point contained in the region. Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.
			}
			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?  Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better... let's discuss next call}}
		\label{fig:lovasz-links}
	\end{center}
\end{figure}

@@

\subsection{Trimming a loss}
\label{sec:trim}

@@

\subsection{Minimum representative sets and non-redundancy}
\label{sec:min-rep-sets-trim}

@@

\subsection{A property elicitation perspective on trimmed losses}
\label{sec:prop-trim}

@@

Perhaps the most pressing open direction is simply to apply our framework to prediction problems of interest.
We hope that the discussion in \S~\ref{sec:apply-embedd-fram}, and the detailed examples in subsequent works, serve as useful guidelines for doing so.
A particularly promising domain to apply our framework is structured prediction, where relatively few consistent surrogates are known.
Indeed, our framework has already been applied to submodular structured problems (\S~\ref{sec:lovasz-hinge}) and to max-margin losses~\cite{nowak2022consistency}.

@@

It can be important for applications to understand the minimum prediction dimension $d$ of a consistent convex surrogate $L:\reals^d\to \reals^\Y_+$ for a given target problem, also called its convex elicitation complexity~\cite{frongillo2021elicitation}.
% The prediction dimension of a surrogate $L : \reals^d \to \reals^\Y_+$ is the $d$ in its definition: the dimension of the surrogate report space.
Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, with prediction dimension $d = n := |\Y|$.
In some settings, such as structured prediction and information retrieval, a prediction dimension of $d=n$ can be prohibitively large.
For example, in \S~\ref{sec:lovasz-hinge} we discuss structured problems which decompose as $k$ simple subproblems, like pixel classification for image segmentation.
The Lov\'asz hinge has prediction dimension $k$ for this problem, whereas our construction would give one with $d = n = 2^k$, an impractical number even for relatively small images.
While one could achieve $d = n-1$ with a simple modification to our construction,\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
it is unclear when and how the prediction dimension could be further lowered.

Beyond studying convex elicitation complexity directly~\citep{ramaswamy2016convex,finocchiaro2021unifying,frongillo2021elicitation},
one promising approach to this question is to first understand the minimum $d$ for which a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$, called the \emph{embedding dimension} of $\ell$, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
One reason this approach may be fruitful is that embeddings have much more structure than general convex losses, such as the fact that calibrated links arise automatically (\S~\ref{thm:thickened-separated}).
Yet from \S~\ref{sec:poly-ie-consistency} and similar observations, it may well be that the lowest possible prediction dimension is achieved by an embedding.

In previous work, we introduce and present some bounds for embedding dimension
based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?  It is the same authors, and same broader project... I think it's less awkward this way, but I'm okay with 3rd person too}.
We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these numbers may always be the same.
It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.

\paragraph{Indirect elicitation as a condition for consistency}
